The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-16 dit-paper_ieee.tex
review

	\subsection{The DBF feasibility test}

	We recall the necessary and sufficient feasability condition on monoprocessor platform given in \cite{baruah1999generalized, baruah1990algorithms} and based on the demand-bound function.

@@

		As explained in \cite{nemhauser1988integer}, a region of $\mathbb{N}_0^n$ such as the C-space can be described by a \emph{polytope}, or a list of parametric linear constraints (called the \emph{formulation}). The constraints must be conditions which can unequivocally decide if a point is included in the region or not. In the sequel we give a formulation for the C-space in $\mathbb{N}_0^n$ (For a formulation in $\mathbb{N}^n$, we can add $C_i \geqslant 1 \; \forall i$ to the list of constraints).

@@

  \begin{remark} (from the definitions):
    \begin{itemize}
      \item Contrary to other idle times, DITs are independent of the
      scheduling or the execution times of the jobs.
      \item In a feasible system, every DIT is an idle time.
      \item In a feasible system, the first DIT happens after the end of the
      first busy period.
      \item As any $kH$ with $k \geqslant 0$ is a DIT in synchronous systems, we have at least $t_d
      \leqslant H$ in this case.
    \end{itemize}
  \end{remark}

  The value of the first DIT can be found by solving the following modular equation system:
	\[
		t_d = \min
		\left( t \; s.t. \; \forall i \; \exists a_i \in [D_i, T_i]:
			\left\{
				\begin{array}{c}
					t > 0 \\
					t \equiv a_i \; (mod \; T_i) \\
				\end{array}
			\right.
		\right)
	\]
  The authors of \cite{george2009characterization} give a method to solve this system for cases in which periods are pairwise coprime.

@@

		As in the synchronous case, the problem of existence of the FPDIT
		can be written as a system of modular equations:
		\[
			\begin{array}{l}
				\exists ? \; t_d \; s.t. \; \forall i \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \; T_i) \\
						a_i \in [D_i, T_i]
					\end{array}
				\right.
			\end{array}
		\]

@@

		The description we presented in Section \ref{sct:cspaceDescr} based on \cite{baruah1999generalized} was general, and
		is thus still relevant. Therefore the C-space is still accurately described by
		the following infinite number of constraints:

>>>>

	\subsection{The DBF feasibility test}
		We recall the necessary and sufficient feasability condition on monoprocessor
		platforms based on the demand-bound function \cite{baruah1999generalized,
		baruah1990algorithms}.

@@

			As explained in \cite{nemhauser1988integer}, a region of $\mathbb{N}_0^n$
			such as the C-space can be described by a \emph{polytope}, or a list of
			parametric linear constraints (called the \emph{formulation}). The
			constraints must be conditions which can unequivocally decide if a point is
			included in the region or not. In the sequel we give a formulation for the
			C-space in $\mathbb{N}_0^n$ (For a formulation in $\mathbb{N}^n$, we can add
			$C_i \geqslant 1 \; \forall \tau_i \in \tau$ to the list of constraints).

@@

		\begin{remark} (from the definitions):
			\begin{itemize}
				\item Contrary to other idle times, DITs are independent of the
					scheduling or the execution times of the jobs.
				\item In a feasible system, every DIT is an idle time.
				\item In a feasible system, the first DIT happens after the end of the
					first busy period.
				\item In synchronous systems any $kH$ with $k \geqslant 0$ is a DIT and we
					also have at least $t_d \leqslant H$.
			\end{itemize}
		\end{remark}

  The value of the first DIT can be found by solving the following modular equation system:
	\[
		t_d = \min
		\left( t \; s.t. \; \forall \tau_i \in \tau, \; \exists a_i \in [D_i, T_i]:
			\left\{
				\begin{array}{c}
					t > 0 \\
					t \equiv a_i \; (mod \; T_i) \\
				\end{array}
			\right.
		\right)
	\]
  The authors of \cite{george2009characterization} give a method to solve this system for cases in which periods are pairwise coprime.

@@

		As in the synchronous case, the problem of existence of the FPDIT
		can be written as a system of modular equations:
		\[
			\begin{array}{l}
				\exists ? \; t_d \; s.t. \; \forall \tau_i \in \tau \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \; T_i) \\
						a_i \in [D_i, T_i]
					\end{array}
				\right.
			\end{array}
		\]

@@

		The description we presented in Section \ref{sct:cspaceDescr} was general, and
		is thus still relevant. Therefore the C-space is still accurately described by
		the following infinite number of constraints:
